\cvsection{Experience}

\begin{cventries}

\cventry
  {Internship – Academic Communication Automation with AI (n8n)}
  {Universidad Andrés Bello}
  {Viña del Mar, Chile}
  {Aug 2025 – Dec 2025}
  {
    \begin{cvitems}
      \item {Developed automated workflows using n8n to support the creation and dissemination of academic announcements.}
      \item {Implemented automation to generate content adapted to different social networks (LinkedIn, Instagram, etc.).}
      \item {Integrated AI to automatically select the most appropriate social network and generate post text depending on the type of announcement.}
      \item {Logged and stored publication history in a database, enabling traceability and future queries.}
      \item {Optimized the publishing process by reducing manual tasks and improving consistency in digital communications.}
    \end{cvitems}
    \vspace{5mm}
  }

\cventry
  {Professional Internship – Vibe Coding Research and AI Model Evaluation}
  {Instituto de Tecnología para la Innovación en Salud y Bienestar (ITISB)}
  {Remote}
  {Jan 2026 – Mar 2026}
  {
    \begin{cvitems}
      \item {Conducted applied research on the Vibe Coding methodology, analyzing advantages, disadvantages, and use cases in software development.}
      \item {Performed comparative evaluation of different AI models for programming and code generation tasks.}
      \item {Designed and executed evaluation pipelines considering code quality, productivity, efficiency, and robustness.}
      \item {Documented results and produced conclusions focused on best practices and implementation recommendations.}
    \end{cvitems}
    \vspace{5mm}
  }
\end{cventries}