\cvsection{Highlighted Projects}

\begin{cventries}

\cventry
  {Machine Learning}
  {Thesis – Academic Trajectory Analysis and Selection of Educational Areas}
  {}
  {}
  {
    \begin{cvitems}
      \item {Analyzed longitudinal data on student academic performance.}
      \item {Developed classification models to predict macro educational areas.}
      \item {Applied supervised Machine Learning techniques and evaluated performance using metrics such as F1-score.}
      \item {Used SHAP for interpretability and analysis of relevant variables.}
      \item {Focused on non-deterministic statistical associations between academic performance and future educational choices.}
    \end{cvitems}
    \vspace{5mm}
  }

\cventry
  {Fullstack}
  {Citizen Security Reporting System – Viña del Mar}
  {}
  {}
  {
    \begin{cvitems}
      \item {Developed a web platform for reporting and visualizing citizen security incidents.}
      \item {Implemented an interactive frontend with dynamic maps using Leaflet and OpenStreetMap.}
      \item {Designed the complete workflow for report creation, storage, and visualization.}
      \item {Built a scalable architecture prepared for backend integration with FastAPI.}
      \item {Managed data using JSON files and prepared the system for future database persistence.}
    \end{cvitems}
    \vspace{5mm}
  }
\cventry
  {Fullstack | GIS | Data Visualization}
  {Territorial Intelligence Platform for Public Safety}
  {}
  {}
  {
    \begin{cvitems}
      \item {Developed a web platform for geospatial reporting and visualization of public safety incidents.}
      \item {Implemented interactive maps and heatmaps using Leaflet and OpenStreetMap to identify incident hotspots.}
      \item {Designed an anonymous reporting system with moderation workflows, validation, and administrative management.}
      \item {Integrated Supabase for authentication, PostgreSQL database, storage, and Row-Level Security (RLS).}
      \item {Designed a scalable full-stack architecture to support municipal decision-making through real-time spatial analytics and data visualization.}
    \end{cvitems}
    \vspace{5mm}
  }
\cventry
  {Machine Learning}
  {Concrete Strength Prediction}
  {}
  {}
  {
    \begin{cvitems}
      \item {Developed predictive models to estimate concrete strength based on physicochemical variables.}
      \item {Applied regression techniques and neural networks using TensorFlow and Keras.}
      \item {Conducted exploratory data analysis, feature selection, and comparative model evaluation.}
      \item {Optimized hyperparameters through systematic search.}
    \end{cvitems}
    \vspace{5mm}
  }

\cventry
  {Machine Learning}
  {CS:GO Player Performance Analysis}
  {}
  {}
  {
    \begin{cvitems}
      \item {Implemented supervised models to analyze competitive performance.}
      \item {Applied K-Means clustering to segment players based on behavior and playstyle.}
      \item {Detected outliers and used libraries such as pandas and scikit-learn for analysis and visualization.}
    \end{cvitems}
    \vspace{5mm}
  }

\cventry
  {Web Application}
  {Production Management System}
  {}
  {}
  {
    \begin{cvitems}
      \item {Developed a system for managing production processes and resources.}
      \item {Implemented backend API and business logic for operational data handling.}
      \item {Designed a modular structure oriented toward scalability.}
      \item {Managed CRUD operations and domain entity modeling.}
    \end{cvitems}
    \vspace{5mm}
  }
  
\cventry
  {Fullstack}
  {E-commerce System – Online Store Platform}
  {}
  {}
  {
    \begin{cvitems}
      \item {Developed a complete web system for online sales management.}
      \item {Implemented backend using Laravel, including authentication, user management, and business logic.}
      \item {Developed CRUD features for products, orders, and administration.}
      \item {Integrated frontend and structured the system using MVC architecture.}
    \end{cvitems}
    \vspace{5mm}
  }

\end{cventries}